XOR-Some Prolific Pilot 2

### 2021-04-26 analysis/xor-some-prolific-pilot2.Rmd
adding QR decomposition for sampling efficiency

Maximal models on raw ratings:
```{r, results='hide'}
# xor, maximal model with interactions and maximal REs
model_xor <- brm(
  target ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

>>>>

Maximal models on raw ratings:
```{r, results='hide'}
# xor, maximal model with interactions and maximal REs
model_xor <- brm(
  bf(target ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
    decomp = "QR"
  ), 
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```
